Vision-Based Automatic Landing of Drones

### 2024-10-21 Article/Article.tex
Add Movement Detection section

@@

\newpage \section{Related Work} \label{sec:related}

\subsection{Obstacle Avoidance}
Obstacle avoidance is a critical aspect of autonomous drone operations, especially in dynamic environments where both static and moving obstacles are present. One approach is integrating depth images with an occupancy voxel map to detect and track dynamic obstacles \cite{xu2023real}. This approach effectively balances computational efficiency with the need for accurate detection and tracking, making it suitable for real-time UAV operations. Another approach involves deep learning techniques like the YOLO (You Only Look Once) framework, which excels at real-time obstacle detection in dynamic environments \cite{redmon2017yolo9000}. YOLO9000 enables rapid detection of multiple objects, making it ideal for fast decision-making in complex surroundings. Its efficiency and accuracy have made it a popular choice for enhancing UAV obstacle avoidance systems.

\section{Drone Control Mechanisms} \label{sec:framework}
The drone’s movement is governed by four fundamental control parameters: yaw, pitch, roll, and throttle. These parameters allow the drone to maneuver in 3D space with precision, facilitating both object tracking and navigation during various flight operations.\\
\begin{description}
\item $\bullet$ Yaw - controls the rotation around the vertical axis, allowing the drone to turn left or right to face objects.
\item $\bullet$ Pitch - adjusts the forward and backward tilt, moving the drone in those directions.
\item $\bullet$ Roll - manages side-to-side tilt, shifting the drone left or right.
\item $\bullet$ Throttle - regulates altitude by increasing or decreasing the drone’s lift.
\end{description}

\section{Framework} \label{sec:framework}
\subsection{Speech Recognition}
The speech recognition system, powered by Google Speech Recognition, continuously listens for the user’s voice until it detects the wake word "hey rexi." Once activated, the system checks subsequent speech for commands from the predefined list, enabling real-time control of the drone without touching the screen. This approach allows the system to remain responsive while minimizing unnecessary processing, facilitating a hands-free operation experience.

@@

\end{description}
\subsection{Object Tracking?}
\subsection{Landing Algorithm}
\subsection{Movement Detection}

\section{Discussion} \label{sec:discussion}

Advancements in language recognition technologies have been noteworthy, yet they confront several challenges and limitations. This discussion highlights some of the prevalent issues:

\begin{enumerate}

    \item \textbf{Linguistic Ambiguity.} Distinguishing between languages with shared linguistic traits

    \item \textbf{Code-Switching Phenomenon.} In multilingual settings,

\end{enumerate}

>>>>

\section{Related Work} \label{sec:related}
\subsection{Obstacle Avoidance}
Obstacle avoidance is a critical aspect of autonomous drone operations, especially in dynamic environments where both static and moving obstacles are present. One approach is integrating depth images with an occupancy voxel map to detect and track dynamic obstacles \cite{xu2023real}. This approach effectively balances computational efficiency with the need for accurate detection and tracking, making it suitable for real-time UAV operations. Another approach involves deep learning techniques like the YOLO (You Only Look Once) framework, which excels at real-time obstacle detection in dynamic environments \cite{redmon2017yolo9000}. YOLO9000 enables rapid detection of multiple objects, making it ideal for fast decision-making in complex surroundings. Its efficiency and accuracy have made it a popular choice for enhancing UAV obstacle avoidance systems.

\section{Drone Control Mechanisms} \label{sec:mechanisms}
The drone’s movement is governed by four fundamental control parameters: yaw, pitch, roll, and throttle. These parameters allow the drone to maneuver in 3D space with precision, facilitating both object tracking and navigation during various flight operations.\\
\begin{description}
\item $\bullet$ Yaw - controls the rotation around the vertical axis, allowing the drone to turn left or right to face objects.
\item $\bullet$ Pitch - adjusts the forward and backward tilt, moving the drone in those directions.
\item $\bullet$ Roll - manages side-to-side tilt, shifting the drone left or right.
\item $\bullet$ Throttle - regulates altitude by increasing or decreasing the drone’s lift.
\end{description}

@@

\section{Movement Detection}
An important aspect of this project is the integration of movement detection, designed to enhance the drone’s functionality as a surveillance tool. Once the drone has landed on a designated edge, it operates as a stationary surveillance camera. In this mode, the system continuously monitors the surrounding environment for movement.\\

Movement detection is implemented using the YOLO (You Only Look Once) object detection framework, which enables real-time identification of objects such as people, vehicles, or other moving entities. When movement is detected, the system immediately alerts the user through the app. This alert includes both a voice notification, specifying what has been detected, and a text message displayed on the screen. These alerts provide real-time updates, enabling timely responses to any potential security concerns.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.7\textwidth]{movementDetect.jpeg}  % Reduced the size here
    % \caption{Guardian mode activated.}
    \label{fig:movementDetect.}
\end{figure}

\section{Speech Recognition} \label{sec:SpeechRecognition}
The speech recognition system, powered by Google Speech Recognition, continuously listens for the user’s voice until it detects the wake word "hey rexi." Once activated, the system checks subsequent speech for commands from the predefined list, enabling real-time control of the drone without touching the screen. This approach allows the system to remain responsive while minimizing unnecessary processing, facilitating a hands-free operation experience.

@@

\end{description}

% \section{Discussion} \label{sec:discussion}

% Advancements in language recognition technologies have been noteworthy, yet they confront several challenges and limitations. This discussion highlights some of the prevalent issues:

% \begin{enumerate}

%     \item \textbf{Linguistic Ambiguity.} Distinguishing between languages with shared linguistic traits

%     \item \textbf{Code-Switching Phenomenon.} In multilingual settings,

% \end{enumerate}
